---
title: "Foraging_analysis_physical"
author: "Shruthi Sukumar"
date: "2024-07-24"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(dplyr)
library(tidyr)
library(lme4)
library(lmerTest)
library(sjPlot)
library(emmeans)
```

## Data import

```{r}
har_dur_df = read.csv('har_dur_shortfirst.csv', header = TRUE)
har_dur_df$env = as.factor(har_dur_df$env)
levels(har_dur_df$env)[1] = "short_travel"
levels(har_dur_df$env)[2] = "long_travel"


har_dur_df = har_dur_df %>% mutate(shortFirst = TRUE)


har_dur_df_lf = read.csv('har_dur_longfirst.csv', header = TRUE)
har_dur_df_lf$env = as.factor(har_dur_df_lf$env)
levels(har_dur_df_lf$env)[1] = "long_travel"
levels(har_dur_df_lf$env)[2] = "short_travel"
har_dur_df_lf = har_dur_df_lf %>% mutate(shortFirst = FALSE)

har_dur_df = rbind(har_dur_df, har_dur_df_lf)

#Exclude subject 65de3fafab17ebda9cb762aa . They only stayed in the same tree in each environment. 
har_dur_df = har_dur_df[har_dur_df$subject != '65de3fafab17ebda9cb762aa',] 

har_dur_df = har_dur_df %>% group_by(subject) %>% mutate(avg_harvest_rate = score_tree/(harvest_dur/1000))


st.err = function(x){
  return(sd(x, na.rm=TRUE)/sqrt(length(x)) )
}

```

## Analysis

1. Number of harvests as a function of time, separated by environment type


```{r}
har_dur_df_sf = har_dur_df[har_dur_df$shortFirst == TRUE,]
har_dur_df_lf = har_dur_df[har_dur_df$shortFirst == FALSE,]

ggplot(data= har_dur_df_sf) + geom_line(aes(x = tree, y = num_harvests, color = env))+
  facet_wrap(~subject, nrow=3, scales = "free_x")+
  xlab("Tree") + ylab("# of Harvests")+
  ggtitle("Short Travel First")+
  theme_classic()

ggplot(data= har_dur_df_lf) + geom_line(aes(x = tree, y = num_harvests, color = env))+
  facet_wrap(~subject, nrow=3, scales = "free_x")+
  xlab("Tree") + ylab("# of Harvests")+
  ggtitle("Long Travel First")+
  theme_classic()

```
Difficulty at exit 
```{r}
har_dur_df_sf = har_dur_df[har_dur_df$shortFirst == TRUE,]

ggplot(data= har_dur_df_sf) + geom_line(aes(x = tree, y = difficulty_at_exit, color = env))+
  facet_wrap(~subject, nrow=3, scales = "free_x")+
  xlab("Tree") + ylab("Difficulty at exit")+
  ggtitle("Short Travel First")+
  theme_classic()

ggplot(data= har_dur_df_lf) + geom_line(aes(x = tree, y = difficulty_at_exit, color = env))+
  facet_wrap(~subject, nrow=3, scales = "free_x")+
  xlab("Tree") + ylab("Difficulty at exit")+
  ggtitle("Long Travel First")+
  theme_classic()

```

Num harvest by patch type 

```{r}
ggplot(data= har_dur_df_sf) + geom_point(aes(x = tree_type, y = num_harvests, color = env))+
  facet_wrap(shortFirst~subject,scales = "free")+
  xlab("Tree Type") + ylab("# of Harvests")+
  ggtitle("Short Travel First")+
  theme_classic()

ggplot(data= har_dur_df_lf) + geom_point(aes(x = tree_type, y = num_harvests, color = env))+
  facet_wrap(shortFirst~subject,scales = "free")+
  xlab("Tree Type") + ylab("# of Harvests")+
  ggtitle("Long Travel First")+
  theme_classic()
```

3. Aggregate data to look at behavior between patches

```{r}
har_dur_agg = har_dur_df %>% group_by(env, tree_type, shortFirst) %>% summarise(mean_num_harvests = mean(num_harvests), sd_num_harvests = sd(num_harvests), mean_harvest_dur = mean(harvest_dur), sd_harvest_dur = sd(harvest_dur), mean_difficulty_exit = mean(difficulty_at_exit), sd_difficulty_exit = sd(difficulty_at_exit)) 

har_dur_agg = har_dur_agg %>% mutate(num_harvests_min = mean_num_harvests - sd_num_harvests, num_harvests_max = mean_num_harvests + sd_num_harvests, harvest_dur_min = mean_harvest_dur - sd_harvest_dur, harvest_dur_max = mean_harvest_dur + sd_harvest_dur, difficulty_exit_min = mean_difficulty_exit - sd_difficulty_exit, difficulty_exit_max = mean_difficulty_exit + sd_difficulty_exit)


har_dur_agg_sf = har_dur_agg[har_dur_agg$shortFirst==TRUE,]
ggplot(data=har_dur_agg_sf) + geom_line(aes(x = tree_type, y = mean_num_harvests, color = env, group = env), width = 0, position = position_dodge(width=0.2))+
  geom_errorbar(aes(x = tree_type, ymin = num_harvests_min, ymax = num_harvests_max, color =env), width = 0, position = position_dodge(width=0.2))+
  xlab("Tree Type") + ylab("Number of Harvests")+
    ggtitle("Short Travel First")+
  theme_classic()

har_dur_agg_lf = har_dur_agg[har_dur_agg$shortFirst==FALSE,]
ggplot(data=har_dur_agg_lf) + geom_line(aes(x = tree_type, y = mean_num_harvests, color = env, group = env), width = 0, position = position_dodge(width=0.2))+
  geom_errorbar(aes(x = tree_type, ymin = num_harvests_min, ymax = num_harvests_max, color =env), width = 0, position = position_dodge(width=0.2))+
  xlab("Tree Type") + ylab("Number of Harvests")+
    ggtitle("Long Travel First")+
  theme_classic()

```
4. Harvest Duration as a function of time, separated by environment type

```{r}
ggplot(data= har_dur_df_sf) + geom_line(aes(x = tree, y = harvest_dur, color = env))+
  facet_wrap(shortFirst~subject, nrow=3, scales = "free_x")+
  xlab("Tree") + ylab("Harvest Duration (ms)")+
  ggtitle("Short Travel First")+
  theme_classic()

ggplot(data= har_dur_df_lf) + geom_line(aes(x = tree, y = harvest_dur, color = env))+
  facet_wrap(shortFirst~subject, nrow=3, scales = "free_x")+
  xlab("Tree") + ylab("Harvest Duration (ms)")+
  ggtitle("Long Travel First")+
  theme_classic()
```
5. Harvest Duration aggregate data 

```{r}
ggplot(data=har_dur_agg_sf) + geom_line(aes(x = tree_type, y = mean_harvest_dur, color = env, group = env), width = 0, position = position_dodge(width=0.2))+
  geom_errorbar(aes(x = tree_type, ymin = harvest_dur_min, ymax = harvest_dur_max, color =env), width = 0, position = position_dodge(width=0.2))+
  xlab("Tree Type") + ylab("Harvest Duration")+
    ggtitle("Short Travel First")+theme_classic()


ggplot(data=har_dur_agg_lf) + geom_line(aes(x = tree_type, y = mean_harvest_dur, color = env, group = env), width = 0, position = position_dodge(width=0.2))+
  geom_errorbar(aes(x = tree_type, ymin = harvest_dur_min, ymax = harvest_dur_max, color =env), width = 0, position = position_dodge(width=0.2))+
  xlab("Tree Type") + ylab("Harvest Duration")+
    ggtitle("Long Travel First")+theme_classic()
```

## normalize metrics by subject 

```{r}
har_dur_df = har_dur_df %>% group_by(subject) %>% mutate(norm_harvest_dur = harvest_dur / mean(harvest_dur, na.rm=TRUE), norm_num_harvests = num_harvests/mean(num_harvests, na.rm=TRUE))

har_dur_agg_norm = har_dur_df %>% group_by(env, tree_type, shortFirst) %>% summarise(mean_norm_num_harvests = mean(norm_num_harvests), sd_norm_num_harvests = sd(norm_num_harvests), mean_norm_harvest_dur = mean(norm_harvest_dur), sd_norm_harvest_dur= sd(norm_harvest_dur)) 

har_dur_agg_norm = har_dur_agg_norm %>% mutate(norm_harvest_dur_min = mean_norm_harvest_dur - sd_norm_harvest_dur, norm_harvest_dur_max = mean_norm_harvest_dur + sd_norm_harvest_dur, norm_num_harvests_min = mean_norm_harvest_dur - sd_norm_harvest_dur, norm_num_harvests_max = mean_norm_harvest_dur + sd_norm_harvest_dur)

har_dur_agg_norm_sf =har_dur_agg_norm[har_dur_agg_norm$shortFirst == TRUE,]

plt_har_dur_sf <- ggplot(data=har_dur_agg_norm_sf) + geom_line(aes(x = tree_type, y = mean_norm_harvest_dur, color = env, group = env), position = position_dodge(width=0.2))+
  geom_errorbar(aes(x = tree_type, ymin = norm_harvest_dur_min, ymax = norm_harvest_dur_max, color =env), width = 0, position = position_dodge(width=0.2))+
  xlab("Tree Type") + ylab("Normalized Harvest Duration")+
    ggtitle("Short Travel First")+
  theme_classic()+
  theme(legend.position="none")

ggsave("plt_har_dur_sf.pdf", plt_har_dur_sf, width = 5, height = 4)
ggsave("plt_har_dur_sf.png", plt_har_dur_sf, width = 5, height = 4)


plt_num_har_sf <- ggplot(data=har_dur_agg_norm_sf) + geom_line(aes(x = tree_type, y = mean_norm_num_harvests, color = env, group = env), position = position_dodge(width=0.2))+
  geom_errorbar(aes(x = tree_type, ymin = norm_num_harvests_min, ymax = norm_num_harvests_max, color =env), width = 0, position = position_dodge(width=0.2))+
  xlab("Tree Type") + ylab("Normalized # of Harvests")+
    ggtitle("Short Travel First")+
  theme_classic()+
  theme(legend.position="none")

ggsave("plt_num_har_sf.pdf", plt_num_har_sf, width = 5, height = 4)
ggsave("plt_num_har_sf.png", plt_num_har_sf, width = 5, height = 4)

har_dur_agg_norm_lf =har_dur_agg_norm[har_dur_agg_norm$shortFirst == FALSE,]

plt_har_dur_lf <-  ggplot(data=har_dur_agg_norm_lf) + geom_line(aes(x = tree_type, y = mean_norm_harvest_dur, color = env, group = env), position = position_dodge(width=0.2))+
  geom_errorbar(aes(x = tree_type, ymin = norm_harvest_dur_min, ymax = norm_harvest_dur_max, color =env), width = 0, position = position_dodge(width=0.2))+
  xlab("Tree Type") + ylab("Normalized Harvest Duration")+
    ggtitle("Long Travel First")+
  theme_classic()+
  theme(legend.position="none")
ggsave("plt_har_dur_lf.pdf", plt_har_dur_lf, width = 5, height = 4)
ggsave("plt_har_dur_lf.png", plt_har_dur_lf, width = 5, height = 4)

plt_num_har_lf <- ggplot(data=har_dur_agg_norm_lf) + geom_line(aes(x = tree_type, y = mean_norm_num_harvests, color = env, group = env), position = position_dodge(width=0.2))+
  geom_errorbar(aes(x = tree_type, ymin = norm_num_harvests_min, ymax = norm_num_harvests_max, color =env), width = 0, position = position_dodge(width=0.2))+
  xlab("Tree Type") + ylab("Normalized # of Harvests")+
    ggtitle("Long Travel First")+
  theme_classic()+
  theme(legend.position="none")
ggsave("plt_num_har_lf.pdf", plt_num_har_lf, width = 5, height = 4)
ggsave("plt_num_har_lf.png", plt_num_har_lf, width = 5, height = 4)
```
```{r}
# interpret dur_per_harvest elements as arrays 

# from chatgpt  -- it works!! 

# Original string
str <- "[1 ,2 , 3]"
# Remove the square brackets and spaces around commas

string_interpret <- function(str){
  clean_str <- gsub("\\[|\\]|\\s*(,\\s*)", "\\1", str)
  
  # Split the string by commas
  split_str <- unlist(strsplit(clean_str, ","))
  
  # Convert the resulting character vector to a numeric vector
  numeric_array <- as.numeric(split_str)
  return(numeric_array)
}
# Print the resulting numeric array
# print(string_interpret(numeric_array))

```

Converting the column of strings to integer arrays that depict the durations per harvest within each tree

```{r}

har_dur_df = har_dur_df %>% mutate(dur_harvest_arr = lapply(dur_per_harvest, string_interpret),
                                   num_presses_arr = lapply(num_presses, string_interpret))
har_dur_long_df = har_dur_df %>% unnest_longer(c(dur_harvest_arr,num_presses_arr))

har_dur_long_df = har_dur_long_df %>% group_by(subject, env, tree) %>% mutate(har_dur_index = row_number(), dur_per_keypress = dur_harvest_arr/num_presses_arr)

har_dur_long_df[har_dur_long_df$dur_per_keypress==0, ]=  NA


```

For each subject, plot the sequence of harvest durations 

```{r}
har_dur_long_df_short = har_dur_long_df[har_dur_long_df$env=='short_travel',]
ggplot(data =har_dur_long_df_short) + geom_line(aes(x = har_dur_index, y= dur_harvest_arr, color = tree_type, group = tree))+
  facet_wrap(shortFirst~subject, nrow = 3, scales="free")+
  # labs(x = "dur_index", y = "Duration Per Harvest", color= "Tree #")+
  theme_classic()

har_dur_long_df_long = har_dur_long_df[har_dur_long_df$env=='long_travel',]
ggplot(data =har_dur_long_df_long) + geom_line(aes(x = har_dur_index, y= dur_harvest_arr, color = tree_type, group = tree))+
  facet_wrap(shortFirst~subject, nrow = 3, scales="free")+
  # labs(x = "dur_index", y = "Duration Per Harvest", color= "Tree #")+
  theme_classic()
```

Summarize the harvest duration 

```{r}

har_dur_long_summ = har_dur_long_df %>% group_by(subject, env, tree_type, har_dur_index, shortFirst) %>% summarise(mean_har_per_dur = mean(dur_harvest_arr, na.rm=TRUE), sd_har_per_dur = sd(dur_harvest_arr, na.rm=TRUE), mean_dur_per_keypress = mean(dur_per_keypress, na.rm=TRUE), sd_dur_per_keypress = sd(dur_per_keypress, na.rm=TRUE) )
har_dur_long_summ = har_dur_long_summ %>% mutate(har_per_dur_min = mean_har_per_dur - sd_har_per_dur, har_per_dur_max = mean_har_per_dur + sd_har_per_dur, dur_per_keypress_min = mean_dur_per_keypress - sd_dur_per_keypress, dur_per_keypress_max = mean_dur_per_keypress + sd_dur_per_keypress)

har_dur_long_summ_sf = har_dur_long_summ[har_dur_long_summ$shortFirst == TRUE,]

ggplot(data = har_dur_long_summ_sf) + geom_line(aes(x = har_dur_index, y = mean_har_per_dur, color = tree_type, group = interaction(tree_type, env), linetype = env ))+
  geom_ribbon(aes(x= har_dur_index, ymin = har_per_dur_min, ymax = har_per_dur_max, fill = tree_type, group = interaction(tree_type, env)), alpha = 0.5)+
  xlab("harvest index") + ylab("Normalized Harvest Duration")+
    ggtitle("Short Travel First")+
  facet_wrap(~subject, scales = "free_x")+
  theme_classic()


har_dur_long_summ_lf = har_dur_long_summ[har_dur_long_summ$shortFirst == FALSE,]

ggplot(data = har_dur_long_summ_lf) + geom_line(aes(x = har_dur_index, y = mean_har_per_dur, color = tree_type, group = interaction(tree_type, env), linetype = env ))+
  geom_ribbon(aes(x= har_dur_index, ymin = har_per_dur_min, ymax = har_per_dur_max, fill = tree_type, group = interaction(tree_type, env)), alpha = 0.5)+
  xlab("harvest index") + ylab("Normalized Harvest Duration")+
    ggtitle("Short Travel First")+
  facet_wrap(~subject, scales = "free_x")+
  theme_classic()

```
Normalizing duration per harvest by number of keypresses 

```{r}


har_dur_long_df_short = har_dur_long_df[har_dur_long_df$env=='short_travel',]
ggplot(data =har_dur_long_df_short) + geom_line(aes(x = har_dur_index, y= dur_per_keypress, color = tree_type, group = tree))+
  facet_wrap(shortFirst~subject, nrow = 3, scales="free")+
  # labs(x = "dur_index", y = "Duration Per Harvest", color= "Tree #")+
  theme_classic()

har_dur_long_df_long = har_dur_long_df[har_dur_long_df$env=='long_travel',]
ggplot(data =har_dur_long_df_long) + geom_line(aes(x = har_dur_index, y= dur_per_keypress, color = tree_type, group = tree))+
  facet_wrap(shortFirst~subject, nrow = 3, scales="free")+
  # labs(x = "dur_index", y = "Duration Per Harvest", color= "Tree #")+
  theme_classic()
```
```{r}


ggplot(data = har_dur_long_summ_sf) + geom_line(aes(x = har_dur_index, y = mean_dur_per_keypress, color = tree_type, group = interaction(tree_type, env), linetype = env ))+
  geom_ribbon(aes(x= har_dur_index, ymin = dur_per_keypress_min, ymax = dur_per_keypress_max, fill = tree_type, group = interaction(tree_type, env)), alpha = 0.5)+
  xlab("harvest index") + ylab("Normalized Harvest Duration")+
    ggtitle("Short Travel First")+
  facet_wrap(~subject, scales = "free")+
  theme_classic()


ggplot(data = har_dur_long_summ_lf) + geom_line(aes(x = har_dur_index, y = mean_dur_per_keypress, color = tree_type, group = interaction(tree_type, env), linetype = env ))+
  geom_ribbon(aes(x= har_dur_index, ymin = dur_per_keypress_min, ymax = dur_per_keypress_max, fill = tree_type, group = interaction(tree_type, env)), alpha = 0.5)+
  xlab("harvest index") + ylab("Normalized Harvest Duration")+
    ggtitle("Short Travel First")+
  facet_wrap(~subject, scales = "free")+
  theme_classic()
```
## Presentation figures 

1. Num harvests and harvest duration for all the data as a function of both the 

```{r}

plt_num_har <- ggplot(data=har_dur_agg_norm) + geom_line(aes(x = tree_type, y = mean_norm_num_harvests, color = env, group = env), width = 0, position = position_dodge(width=0.2))+
  geom_errorbar(aes(x = tree_type, ymin = norm_num_harvests_min, ymax = norm_num_harvests_max, color =env), width = 0, position = position_dodge(width=0.2))+
  xlab("Tree Type") + ylab("Normalized Number of Harvests")+
  theme_classic()+
  theme(legend.position="none") 

ggsave("plt_num_har.pdf", plt_num_har, width = 5, height = 4)
ggsave("plt_num_har.png", plt_num_har, width = 5, height = 4)


plt_har_dur <- ggplot(data=har_dur_agg_norm) + geom_line(aes(x = tree_type, y = mean_norm_harvest_dur, color = env, group = env), width = 0, position = position_dodge(width=0.2))+
  geom_errorbar(aes(x = tree_type, ymin = norm_harvest_dur_min, ymax = norm_harvest_dur_max, color =env), width = 0, position = position_dodge(width=0.2))+
  xlab("Tree Type") + ylab("Normalized Harvest Duration")+
  theme_classic()+
  theme(legend.position="none") 

ggsave("plt_har_dur.pdf", plt_har_dur, width = 5, height = 4)
ggsave("plt_har_dur.png", plt_har_dur, width = 5, height = 4)

```

2. Difficulty at the end of harvest 


```{r}
har_dur_agg_sf = har_dur_agg[har_dur_agg$shortFirst==TRUE,]
ggplot(data=har_dur_agg_sf) + geom_line(aes(x = tree_type, y = mean_difficulty_exit, color = env, group = env), width = 0, position = position_dodge(width=0.2))+
  geom_errorbar(aes(x = tree_type, ymin = difficulty_exit_min, ymax = difficulty_exit_max, color =env), width = 0, position = position_dodge(width=0.2))+
  xlab("Tree Type") + ylab("Difficulty at Exit")+
    ggtitle("Short Travel First")+
  theme_classic()

har_dur_agg_lf = har_dur_agg[har_dur_agg$shortFirst==FALSE,]
ggplot(data=har_dur_agg_lf) + geom_line(aes(x = tree_type, y = mean_difficulty_exit, color = env, group = env), width = 0, position = position_dodge(width=0.2))+
  geom_errorbar(aes(x = tree_type, ymin = difficulty_exit_min, ymax = difficulty_exit_max, color =env), width = 0, position = position_dodge(width=0.2))+
  xlab("Tree Type") + ylab("Number of Harvests")+
    ggtitle("Long Travel First")+
  theme_classic()

```
difficulty for entire aggregate 

```{r}

ggplot(data=har_dur_agg) + geom_line(aes(x = tree_type, y = mean_difficulty_exit, color = env, group = env), width = 0, position = position_dodge(width=0.2))+
  geom_errorbar(aes(x = tree_type, ymin = difficulty_exit_min, ymax = difficulty_exit_max, color =env), width = 0, position = position_dodge(width=0.2))+
  xlab("Tree Type") + ylab("Number of Harvests")+
  theme_classic()

```
```{r}

plt_diff_exit_sf <- ggplot(data=har_dur_agg_sf) + geom_bar(aes(x = env, y = mean_difficulty_exit, fill = env), stat="identity")+
  geom_errorbar(aes(x = env, ymin = difficulty_exit_min, ymax = difficulty_exit_max), width=0)+
  facet_wrap(~tree_type)+
  ggtitle("Short Travel First")+
  xlab("Environment") + ylab("Difficulty at Exit")+
  theme_classic()+theme(legend.position = "none")

ggsave("plt_diff_exit_sf.pdf", plt_diff_exit_sf, width = 5, height = 4)
ggsave("plt_diff_exit_sf.png", plt_diff_exit_sf, width = 5, height = 4)

plt_diff_exit_lf <- ggplot(data=har_dur_agg_lf) + geom_bar(aes(x = env, y = mean_difficulty_exit, fill = env), stat="identity")+
  geom_errorbar(aes(x = env, ymin = difficulty_exit_min, ymax = difficulty_exit_max), width=0)+
  facet_wrap(~tree_type)+
  ggtitle("Long Travel First")+
  xlab("Environment") + ylab("Difficulty at Exit")+
  theme_classic()+theme(legend.position = "none")

ggsave("plt_diff_exit_lf.pdf", plt_diff_exit_lf, width = 5, height = 4)
ggsave("plt_diff_exit_lf.png", plt_diff_exit_lf, width = 5, height = 4)

```

all aggregate data for difficulty at exit

```{r}

har_dur_all_agg = har_dur_df %>% group_by(env, tree_type) %>% summarise(mean_num_harvests = mean(num_harvests), sd_num_harvests = sd(num_harvests), mean_harvest_dur = mean(harvest_dur), sd_harvest_dur = sd(harvest_dur), mean_difficulty_exit = mean(difficulty_at_exit), sd_difficulty_exit = sd(difficulty_at_exit)) 

har_dur_all_agg = har_dur_all_agg %>% mutate(num_harvests_min = mean_num_harvests - sd_num_harvests, num_harvests_max = mean_num_harvests + sd_num_harvests, harvest_dur_min = mean_harvest_dur - sd_harvest_dur, harvest_dur_max = mean_harvest_dur + sd_harvest_dur, difficulty_exit_min = mean_difficulty_exit - sd_difficulty_exit, difficulty_exit_max = mean_difficulty_exit + sd_difficulty_exit)



plt_diff_exit <- ggplot(data=har_dur_all_agg) + geom_bar(aes(x = env, y = mean_difficulty_exit, fill = env), stat="identity")+
  geom_errorbar(aes(x = env, ymin = difficulty_exit_min, ymax = difficulty_exit_max), width=0)+
  facet_wrap(~tree_type)+
  xlab("Environment") + ylab("Difficulty at Exit")+
  theme_classic()+theme(legend.position = "none")
ggsave("plt_diff_exit.pdf", plt_diff_exit, width = 5, height = 4)
ggsave("plt_diff_exit.png", plt_diff_exit, width = 5, height = 4)
```

Individual line plots over aggregate line plot 

```{r}

har_dur_agg_subj = har_dur_df %>% group_by(env, tree_type, subject) %>% 
  summarise(mean_norm_num_harvests = mean(norm_num_harvests), 
            sd_norm_num_harvests = sd(norm_num_harvests), 
            mean_norm_harvest_dur = mean(norm_harvest_dur), 
            sd_norm_harvest_dur= sd(norm_harvest_dur), 
            mean_difficulty_exit = mean(difficulty_at_exit), 
            sd_difficulty_exit = sd(difficulty_at_exit)) 


har_dur_agg_norm = har_dur_agg_subj %>% group_by(env, tree_type) %>% 
  summarise(mean_norm_num_harvests2 = mean(mean_norm_num_harvests), 
            sd_norm_num_harvests2 = st.err(mean_norm_num_harvests), 
            mean_norm_harvest_dur2 = mean(mean_norm_harvest_dur), 
            sd_norm_harvest_dur2= st.err(mean_norm_harvest_dur), 
            mean_difficulty_exit2 = mean(mean_difficulty_exit), 
            sd_difficulty_exit = st.err(mean_difficulty_exit)) 

har_dur_agg_norm = har_dur_agg_norm %>% mutate(norm_harvest_dur_min = mean_norm_harvest_dur2 - sd_norm_harvest_dur2,
                                               norm_harvest_dur_max = mean_norm_harvest_dur2 + sd_norm_harvest_dur2, 
                                               norm_num_harvests_min = mean_norm_num_harvests2 - sd_norm_num_harvests2, 
                                               norm_num_harvests_max = mean_norm_num_harvests2 + sd_norm_num_harvests2,
                                               difficulty_exit_min = mean_difficulty_exit2 - sd_difficulty_exit, 
                                               difficulty_exit_max = mean_difficulty_exit2 + sd_difficulty_exit)

p <- ggplot() + geom_line(data = har_dur_agg_norm,aes(x= tree_type, y = mean_norm_harvest_dur2, color = env, group = env), size = 1)+
  geom_point(data = har_dur_agg_norm, aes(x= tree_type, y = mean_norm_harvest_dur2), size = 4)+
   scale_shape(solid = FALSE)+
  geom_errorbar(data = har_dur_agg_norm,aes(x = tree_type, ymin = norm_harvest_dur_min, ymax = norm_harvest_dur_max, color= env ), width = 0)
p
p = p + geom_line(data = har_dur_agg_subj, aes(x = tree_type, y = mean_norm_harvest_dur, group = interaction(subject, env) ,color= env) , alpha =0.5, size = 0.3)+
  geom_point(data = har_dur_agg_subj, aes(x = tree_type, y = mean_norm_harvest_dur, group = interaction(subject, env) ,color= env), shape = 1, size = 2)+
  xlab("Tree Type")+ ylab("Harvest Duration (norm)")+ theme_classic()+
  theme(legend.position = "none", axis.text=element_text(size=12), axis.title=element_text(size=14,face="bold"))
p

ggsave("plot_norm_har_dur.pdf", p, width = 5, height = 4)
```

```{r}
p <- ggplot() + geom_line(data = har_dur_agg_norm,aes(x= tree_type, y = mean_norm_num_harvests2, color = env, group = env), size = 1)+
  geom_point(data = har_dur_agg_norm, aes(x= tree_type, y = mean_norm_num_harvests2), size = 4)+
   scale_shape(solid = FALSE)+
  geom_errorbar(data = har_dur_agg_norm,aes(x = tree_type, ymin = norm_num_harvests_min, ymax = norm_num_harvests_max, color= env ), width = 0)
p
p = p + geom_line(data = har_dur_agg_subj, aes(x = tree_type, y = mean_norm_num_harvests, group = interaction(subject, env) ,color= env) , alpha =0.5, size = 0.3)+
  geom_point(data = har_dur_agg_subj, aes(x = tree_type, y = mean_norm_num_harvests, group = interaction(subject, env) ,color= env), shape = 1, size = 2)+
  xlab("Tree Type")+ ylab("Number of harvests (norm)")+ theme_classic()+
  theme(legend.position = "none", axis.text=element_text(size=12), axis.title=element_text(size=14,face="bold"))
p
```


```{r}

p <- ggplot() + geom_bar(data = har_dur_agg_norm,aes(x= env, y = mean_norm_harvest_dur2, fill = tree_type), size = 2, alpha = 0.3,position=position_dodge(width = 1), stat="identity")+
  geom_errorbar(data = har_dur_agg_norm,aes(x = env, ymin = norm_harvest_dur_min, ymax = norm_harvest_dur_max, color= tree_type ),position=position_dodge(width = 1), width = 0)
# p
# 
# p = p + geom_line(data = har_dur_agg_subj, aes(x = env, y = mean_norm_harvest_dur, group = interaction(subject, tree_type), alpha =0.5, position = position_dodge(width = 1)))+ theme_classic()+
#   xlab("Tree Type")+ ylab("Harvest Duration (norm)")
p
```
```{r}

p <- ggplot() + geom_bar(data = har_dur_agg_norm,aes(x= env, y = mean_difficulty_exit2, fill = env), size = 2, alpha = 0.3,position=position_dodge(width = 1), stat="identity")+
  geom_errorbar(data = har_dur_agg_norm,aes(x = env, ymin = difficulty_exit_min, ymax = difficulty_exit_max, color= env ),position=position_dodge(width = 1), width = 0)+facet_wrap(~tree_type)

p = p + geom_line(data = har_dur_agg_subj, aes(x = env, y = mean_difficulty_exit
                                               ,color= tree_type, group = interaction(subject, tree_type) ) , alpha =0.5, size = 0.3)+
  geom_point(data = har_dur_agg_subj, aes(x = env, y = mean_difficulty_exit ,color= env), shape = 1, size = 2)+
  facet_wrap(~tree_type)+
  xlab("Tree Type")+ ylab("Harvest Difficulty at Exit")+ theme_classic()+
  theme(legend.position = "none", axis.text=element_text(size=12), axis.title=element_text(size=14,face="bold"))
p
ggsave("plot_har_difficulty.pdf", p, width = 5, height = 4)
```

Statistics for the different quantities 

- instead of plotting the normalized responses, plot the estimated marginal means based on covariates added

Formula:

harvest duration ~ 1 + patch_type*env_type + (1|Subject) 


```{r}
har_dur_df$harvest_dur_scaled = har_dur_df$harvest_dur/1000
mdl_har_duration = lmer(data= har_dur_df, harvest_dur_scaled ~ env * tree_type + (1|subject))
summary(mdl_har_duration)
plot_model(mdl_har_duration, type="diag")
```
Estimated marginal means and corresponding plot 

```{r}
EMM.env = emmeans(mdl_har_duration, "env")
```


Statistical modelling for number of harvests metric 

Reasons for separating the two metrics :
- harvest duration should be correlated with number of harvests
- Subjects have the ability to adjust the time taken for subsequent harvests 

```{r}

mdl_num_harvests = lmer(data= har_dur_df, num_harvests ~ env * tree_type + (1|subject))
summary(mdl_num_harvests)
plot_model(mdl_num_harvests, type="diag")
```


Harvest Rate at the end of harvest 

```{r}

ggplot(data= har_dur_df_sf) + geom_line(aes(x = tree, y = avg_harvest_rate, color = env))+
  facet_wrap(shortFirst~subject, nrow=3, scales = "free")+
  xlab("Tree") + ylab("Harvest Duration (ms)")+
  ggtitle("Short Travel First")+
  theme_classic()

ggplot(data= har_dur_df_lf) + geom_line(aes(x = tree, y = avg_harvest_rate, color = env))+
  facet_wrap(shortFirst~subject, nrow=3, scales = "free_x")+
  xlab("Tree") + ylab("Harvest Duration (ms)")+
  ggtitle("Long Travel First")+
  theme_classic()
```

a`
 